Capstone Movielens Report

### 2025-05-18 reports/capstone-movielens.site/02.5.UME-model.Rmd

#### `calc_user_movie_effect_RMSE.cv` Function
\

@@

UME.rglr.fine_tune.RMSE.best <- UME.rglr.fine_tune.results$best_result["best_RMSE"]
```
```{r}
writeLines("*** Fine-tuning results object data structure ***")
str(UME.rglr.fine_tune.results)
writeLines("--------")
writeLines('')

writeLines("*** Fine-tuning: best results ***")
UME.rglr.fine_tune.results$best_result
writeLines("------")
writeLines('')

writeLines("*** Fine-tuning: best parameter value ***")
UME.rglr.fine_tune.RMSE.best
```

@@

Finally, we retrain our model with the best $\lambda$ parameter value we have just figured out:
```{r, eval=FALSE}
  UME.rglr.best_lambda <- best_result["param.best_value"]
  UME.rglr.best_lambda

  rglr.UM_effect <- train_user_movie_effect(edx, UME.rglr.best_lambda)

```
```{r, echo=FALSE}
writeLines("*** The Best Fine-tuning Results ***")
UME.rglr.fine_tune.results$best_result

writeLines("*** Regularized User+Movie Effect Structure ***")
str(rglr.UM_effect)
```

@@

Finally, after _Regularization_, we obtained the following result:
```{r, eval=FALSE}
UME.rglr.retrain.RMSE <- calc_user_movie_effect_RMSE.cv(rglr.UM_effect)

RMSEs.ResultTibble.rglr.UME <- RMSEs.ResultTibble.UME |> 
  RMSEs.AddRow("Regularized User+Movie Effect Model", 
               UME.rglr.retrain.RMSE,
               comment = "Computed for `lambda` = %1" |>
                 msg.glue(UME.rglr.best_lambda))
```
```{r, echo=FALSE}
print_log1("Regularized User+Movie Effect Model has been re-trained for the best `lambda`: %1.",
         UME.rglr.best_lambda)
print_log1("The best RMSE after being regularized: %1",
         UME.rglr.retrain.RMSE)
```
```{r}
RMSE_kable(RMSEs.ResultTibble.rglr.UME)
```

>>>>

#### `calc_user_movie_effect_RMSE.cv` Function { #func.calc_user_movie_effect_RMSE.cv }
\

@@

UME.rglr.fine_tune.RMSE.best <- UME.rglr.fine_tune.results$best_result["best_RMSE"]
```
```{r, echo=FALSE}
writeLines("*** Fine-tuning results object data structure ***")
str(UME.rglr.fine_tune.results)

writeLines("*** Fine-tuning: best results ***")
UME.rglr.fine_tune.results$best_result
```

@@

Now, we can calculate the _Regularized User+Movie Effect_ by retraining our model on the entire `edx` dataset with the best value of the $\lambda$ parameter we just calculated, for the definitive _Root Mean Squared Error_ calculation and use in subsequent models.
```{r, eval=FALSE}
  UME.rglr.best_lambda <- best_result["param.best_value"]
  UME.rglr.best_lambda

  rglr.UM_effect <- train_user_movie_effect(edx, UME.rglr.best_lambda)
```
```{r, echo=FALSE}
writeLines("*** The Best Fine-tuning Results ***")
UME.rglr.fine_tune.results$best_result

writeLines("*** Regularized User+Movie Effect Structure ***")
str(rglr.UM_effect)

print_log1("Regularized User+Movie Effect Model has been re-trained for the best `lambda`: %1.",
         UME.rglr.best_lambda)
```

@@

We calculate the _Root Mean Squared Error_ for the ultimately computed _User+Movie Effect_ using [calc_user_movie_effect_RMSE.cv](#func.calc_user_movie_effect_RMSE.cv) function described above as follows:
```{r, eval=FALSE}
UME.rglr.retrain.RMSE <- calc_user_movie_effect_RMSE.cv(rglr.UM_effect)
```
```{r}
print_log1("The best RMSE after being regularized: %1",
         UME.rglr.retrain.RMSE)
```

Finally, we add the definitive result for the current model to our _Result Table_:
```{r, eval=FALSE}
RMSEs.ResultTibble.rglr.UME <- RMSEs.ResultTibble.UME |> 
  RMSEs.AddRow("Regularized User+Movie Effect Model", 
               UME.rglr.retrain.RMSE,
               comment = "Computed for `lambda` = %1" |>
                 msg.glue(UME.rglr.best_lambda))
```
```{r}
RMSE_kable(RMSEs.ResultTibble.rglr.UME)
```
